\documentclass[helvetica,openbib,totpages,french]{europecv}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage[a4paper,top=1.27cm,left=1cm,right=1cm,bottom=2cm]{geometry}
\usepackage[french]{babel}
\usepackage{bibentry}
\usepackage{url}

\renewcommand{\ttdefault}{phv} % Uses Helvetica instead of fixed width font

\ecvname{Cossou, Christophe}
%\ecvfootername{Name Surname}
\ecvaddress{69, rue anatole france ; 33150 CENON}
\ecvtelephone[06 02 26 97 63]{05 33 51 98 13}
%\ecvtelephone[portable (Remove if not relevant)]{fixe (Remove if not relevant)}

%\ecvfax{(Remove if not relevant)}
\ecvemail{\url{ccossou@gmail.com}}
\ecvnationality{Française}
\ecvdateofbirth{28/06/1986}
\ecvgender{Masculin}
%\ecvpicture[width=2cm]{mypicture}
\ecvfootnote{For more information go to \url{http://europass.cedefop.eu.int}\\
\textcopyright~European Communities, 2003.}

\begin{document}
\selectlanguage{french}


\begin{europecv}
\ecvpersonalinfo%[5pt]

\ecvitem[.5em]{\ecvSectionStyle{Emploi recherché}}{\large\textbf{Consultant}}

\ecvsection{Expérience professionnelle}
\ecvitem{Dates}{Add separate entries for each relevant post occupied, starting from the most recent. (Remove if not relevant).}
\ecvitem{Occupation or position held}{\ldots}
\ecvitem{Main activities and responsibilities}{\ldots}
\ecvitem{Name and address of employer}{\ldots}
\ecvitem{Type of business or sector}{\ldots}

\ecvsection{Éducation et Formation}

\ecvitem{Dates}{Add separate entries for each relevant course you have completed, starting from the most recent. (Remove if not relevant).}
\ecvitem{Title of qualification awarded}{\ldots}
\ecvitem{Principal subjects/Occupational skills covered}{\ldots}
\ecvitem{Name and type of organization providing education and training}{\ldots}
\ecvitem{Level in national or international classification\footnote{If appropriate.}}{\ldots}

\ecvsection{Compétences personnelles}

\ecvmothertongue[5pt]{Français}
\ecvitem{\large Autre(s) langue(s)}{}
\ecvlanguageheader{(*)}
\ecvlanguage{Anglais}{\ecvCOne}{\ecvCOne}{\ecvCOne}{\ecvCOne}{\ecvBTwo}
\ecvlanguage{Espagnol}{\ecvATwo}{\ecvATwo}{\ecvAOne}{\ecvAOne}{\ecvAOne}
\ecvlanguagefooter[10pt]{(*)}

\ecvitem[10pt]{\large Compétences en communication}{Replace this text by a description of these competences and indicate where they were acquired (remove if not relevant).}
\ecvitem[10pt]{\large Compétences organisationnelles/managériales}{Replace this text by a description of these competences and indicate where they were acquired (remove if not relevant).}
\ecvitem[10pt]{\large Compétences liées à l'emploi}{Replace this text by a description of these competences and indicate where they were acquired (remove if not relevant).}
\ecvitem[10pt]{\large Compétences informatiques}{Replace this text by a description of these competences and indicate where they were acquired (remove if not relevant).}
\ecvitem[10pt]{\large Autres compétences}{Replace this text by a description of these competences and indicate where they were acquired (remove if not relevant).}
\ecvitem{\large Permis de conduire}{State here whether you hold a driving licence and if so for which categories of vehicle. (Remove if not relevant).}

\ecvsection{Information complémentaire}
\ecvitem[10pt]{}{Include here any other information that may be relevant, for example contact persons, references, etc. (Remove heading if not relevant).}
\bibliographystyle{plain}
\nobibliography{publications}
\ecvitem{}{\textbf{Publications}}
\ecvitem{}{\bibentry{pub1}}
\ecvitem[10pt]{}{\bibentry{pub2}}
\ecvitem{}{\textbf{Personal interests}}
\ecvitem{}{\ldots}

\ecvsection{Annexes}
\ecvitem{}{List any item attached to the CV}
\end{europecv}


\end{document} 